---
output: html_document
params:
  sex: "Both Sexes, "
  dat: "../r2_results/geno_correlation_sig.r2"
title: "`r params$sex` LD scores correlation matrix: Clustering"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(plotly)
require(crosstalk)
require(data.table)
require(dplyr)
require(htmltools)
# There should be another data.table that is saved here that is just the lower triangular portion.
corr <- fread(params$dat, key=c("p1", "p2"))
# Then, need to include some descriptions of what I did (in Rmarkdown).
# Links to the other plots on the site.
# Include some Rmarkdown with the table so that it can stand alone as it's own site, rather than being this frame thing.
# Create the same thing as this for the diffusion plot.
# Also, want to include the same thing for the phentotypic correlations.
# Want to center the plots.

# Jobs
# get rid of `irnt`.
# include the phenotypic correlation as a matrix.
# include the difference between them as a matrix.
# also need to incorporate male and female results as separate pages.
# want a phenotype specific table too, which you can naivigate - this won`t be big so can easily include using Raymonds methods.
# want to run UMAP.
# want to run PCA.
# Include all the relevant links to the UK biobank website. 
# Ideally, want the numbers associated to each phenotype...would need to parse the summary file for that.
# Want to add titles etc to the plotly plots that I created that say what everything is.
# Get rid of the gross buttons....or at the very least, figure out how to centre them.

```

Here are the correlations between the UK Biobank phenotypes, restricting to the subset as defined heritability results website.

Rows and columns are ordered by correlation distance using hierarchical clustering using the 'complete' method.

<br>

```{r corr_alphabet, echo=FALSE}
i_max <- length(levels(factor(corr$p1)))+1
phenotypes <- c(corr$p1[1], corr$p2[1:i_max-1])
phenotypes_translation <- c(corr$description_p1[1], corr$description_p2[1:i_max-1])
corr_matrix <- matrix(0, nrow=i_max, ncol=i_max)
p_matrix <- matrix(0, nrow=i_max, ncol=i_max)
h2_matrix <- matrix(0, nrow=i_max, ncol=i_max)
se_matrix <- matrix(0, nrow=i_max, ncol=i_max)

# # Correlation matrix
corr_matrix[lower.tri(corr_matrix)] <- corr$rg
corr_matrix[which(lower.tri(corr_matrix), arr.ind=TRUE)[,c(2,1)]] <- corr$rg
diag(corr_matrix) <- 1

# P-value matrix
p_matrix[lower.tri(p_matrix)] <- corr$p
p_matrix[which(lower.tri(p_matrix), arr.ind=TRUE)[,c(2,1)]] <- corr$p

# h2 matrix
h2_matrix[2:i_max,] <- corr$h2_obs[1:i_max-1]
h2_matrix <- pmin(h2_matrix, t(h2_matrix)) > 0.05

# se matrix
se_matrix[lower.tri(se_matrix)] <- corr$se
se_matrix[which(lower.tri(se_matrix), arr.ind=TRUE)[,c(2,1)]] <- corr$se

div_colors <- c('blue','white','red')

conditions.text <- paste0(outer(phenotypes, phenotypes, paste, sep=" : "), '\n',
						  outer(phenotypes_translation, phenotypes_translation, paste, sep= " : "), '\n',
						  'Correlation: ', signif(corr_matrix, 3), ', p-value: ', signif(p_matrix, 3))
conditions.text <- matrix(conditions.text, nrow=length(phenotypes), ncol=length(phenotypes))

ax <- list(
  title = "",
  zeroline = FALSE,
  showline = FALSE,
  showticklabels = FALSE,
  showgrid = FALSE,
  ticks = ''
)

# Rearrange the rows according to dendrogram.
dd.col <- as.dendrogram(hclust(dist(corr_matrix)))
ord <- order.dendrogram(dd.col)

p <- div(plot_ly(z = corr_matrix[ord, ord],
	colors = colorRamp(div_colors),
	zmin=-1,
	zmax=1,
	type = "heatmap",  hoverinfo='text',
	text = conditions.text[ord, ord],
	width=800, height=700) %>% layout(yaxis=list(autorange='reversed')) %>% layout(xaxis = ax, yaxis = ax), align='center')
p
```

Hovering over the matrix, you can explore the correlations ($r_g$) between pairs of phenotypes, together with their associated $p$-values.

All results are evaluated using LD score correlation regression; ([Bulik-Sullivan et al. 2015](https://www.ncbi.nlm.nih.gov/pubmed/26414676)).

