---
output: html_document
title: "Diffusion Map, using ForceAtlas to display results"
params:
  rerun: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(plotly)

# Uncomment if you need to generate the .Rdata files to plot

if (params$rerun)
{
    require(crosstalk)
    require(data.table)
    require(dplyr)
    require(htmltools)
    require(FNN)
    require(ForceAtlas2)

    corr <- fread("../r2_results/geno_correlation_sig.r2", key=c("p1", "p2"))
    options(warn = -1)

    # Create a function for the diffusion map embedding.
    diffusion_map_embedding <- function(affinity, k, t)
    {
        d <- rowSums(affinity)
        markov <- affinity / d
        ev <- eigen(markov)
        idx <- order(abs(ev$values), decreasing=TRUE)
        e <- ev$values[idx]
        v <- ev$vectors[,idx]

        mat <- matrix(nrow=nrow(affinity), ncol=k)

        for (i in 2:(k+1)) {
            mat[,(i-1)] <- v[,i] * (e[i] ** t)
        }

        return(mat)
    }
}

```

Here we use the squared genetic correlation matrix as the affinity matrix, and compute a Nonlinear dimensionality reduction. We then project this onto the plane using the R package `ForceAtlas`. Points are coloured by the final level of the `path` column in the UK Biobank Data dictionary. Colouring by the second level of the `path` column can be found [here](diffusion_map.html).

<br>

```{r diff_map, echo=FALSE, warning=FALSE}

if (params$rerun){
    # Uncomment to evaluate the embedding, if it has already been generated just load it in.
    storeWarn<- getOption("warn")
    options(warn = -1) 
    i_max <- length(levels(factor(corr$p1)))+1
    phenotypes <- c(corr$p1[1], corr$p2[1:i_max-1])
    phenotypes <- gsub("_irnt", "", phenotypes)
    phenotypes_translation <- c(corr$description_p1[1], corr$description_p2[1:i_max-1])

    # Correlation matrix

    corr_matrix <- matrix(0, nrow=i_max, ncol=i_max)
    rownames(corr_matrix) <- phenotypes
    colnames(corr_matrix) <- phenotypes
    corr_matrix[lower.tri(corr_matrix)] <- corr$rg
    corr_matrix[which(lower.tri(corr_matrix), arr.ind=TRUE)[,c(2,1)]] <- corr$rg
    diag(corr_matrix) <- 1

    corr_matrix <- corr_matrix[order(phenotypes), order(phenotypes)]
    phenotypes <- phenotypes[order(phenotypes)]
    phenotypes_translation <- phenotypes_translation[order(phenotypes)]

    phenotypes_and_categories <- fread("../inputs/Fields_and_categories.tsv") %>% mutate(phenotypes_to_match = FieldID)
    df <- data.table(phenotypes=phenotypes, translation=phenotypes_translation) %>% mutate(phenotypes_to_match = gsub("_.*", "", phenotypes))

    df_merge <- merge(df, phenotypes_and_categories, by='phenotypes_to_match', all.x=TRUE)
    df_merge <- df_merge[order(df_merge$phenotypes),]

    # Using the diffusion map for 40 components, create the weights and use the force atlas package.
    affinity <- corr_matrix ** 2
    diff_embed <- Re(diffusion_map_embedding(affinity, 40, 1))
    nw <- get.knn(diff_embed, k=40)
    df_nw <- data.frame(from=rep(seq(1,nrow(nw$nn.index))), to=as.vector(nw$nn.index), weights=1)

    atlasproj <- layout.forceatlas2(df_nw, directed=FALSE, iterations = 5000, plotstep = 100)
    atlasproj$name <- paste(df_merge$phenotypes, df_merge$translation, sep=" : ")

    where_ICD <- grep("main ICD10", df_merge$translation)
    df_merge$level2cat[where_ICD] <- "ICD10 code"
    df_merge$finallevelcat[where_ICD] <- "ICD10 code"

    where_finngen <- which(is.na(df_merge$level2cat))
    df_merge$level2cat[where_finngen] <- "FinnGen"
    df_merge$finallevelcat[where_finngen] <- "FinnGen"
    
    atlasproj$level2cat <- df_merge$level2cat
    atlasproj$finallevelcat <- df_merge$finallevelcat

    save('atlasproj', file='../Rdata_outputs/atlasproj.Rdata')
}

load('../Rdata_outputs/atlasproj.Rdata')

ax <- list(
  title = "",
  zeroline = FALSE,
  showline = FALSE,
  showticklabels = FALSE,
  showgrid = FALSE,
  ticks = ''
)

# DEV: add in the axis labels.
p <- div(plot_ly(
  atlasproj, x = ~V1, y = ~V2,
  type = 'scatter',
  mode = 'markers',
  # Hover text:
  text = atlasproj$name,
  color = ~factor(finallevelcat), #size = ~carat
  hoverinfo='text',
  width=800, height=800
) %>% layout(xaxis = ax, yaxis = ax), align='center')
p
```
</div>