---
output: html_document
title: "Principal Component Analysis"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Uncomment if you need to generate the .Rdata files to plot
require(plotly)
require(data.table)
require(GGally)
require(dplyr)

corr <- fread("../r2_results/geno_correlation_sig.r2", key=c("p1", "p2"))

i_max <- length(levels(factor(corr$p1)))+1

phenotypes <- c(corr$p1[1], corr$p2[1:i_max-1])
phenotypes <- gsub("_irnt", "", phenotypes)
phenotypes_translation <- c(corr$description_p1[1], corr$description_p2[1:i_max-1])

# Correlation matrix

corr_matrix <- matrix(0, nrow=i_max, ncol=i_max)
corr_matrix[lower.tri(corr_matrix)] <- corr$rg

rownames(corr_matrix) <- phenotypes
colnames(corr_matrix) <- phenotypes

corr_matrix[which(lower.tri(corr_matrix), arr.ind=TRUE)[,c(2,1)]] <- corr$rg
diag(corr_matrix) <- 1

corr_matrix <- corr_matrix[order(phenotypes), order(phenotypes)]
phenotypes <- phenotypes[order(phenotypes)]
phenotypes_translation <- phenotypes_translation[order(phenotypes)]

phenotypes_and_categories <- fread("../inputs/Fields_and_categories.tsv") %>% mutate(phenotypes_to_match = FieldID)
df <- data.table(phenotypes=phenotypes, translation=phenotypes_translation) %>% mutate(phenotypes_to_match = gsub("_.*", "", phenotypes))

df_merge <- merge(df, phenotypes_and_categories, by='phenotypes_to_match', all.x=TRUE)
df_merge <- df_merge[order(df_merge$phenotypes),]
df_merge$level2cat[which(is.na(df_merge$level2cat))] <- "FinnGen"
df_merge$finallevelcat[which(is.na(df_merge$finallevelcat))] <- "FinnGen"

results <- eigen(corr_matrix)

plot_results <- data.frame(evals = results$values, evecs = results$vectors, phenotypes = df_merge$phenotypes,
	level2cat = df_merge$level2cat, finallevelcat = df_merge$finallevelcat, translation=df_merge$translation)


fwrite(corr_matrix, file='../inputs/input_to_UMAP_corr.tsv', row.names=FALSE, col.names=FALSE)
save('plot_results', file='../Rdata_outputs/pca.Rdata')

```

Here we display the first six principal components, plotting each of the first three pairs against each other. Clicking on the various groupings of phenotypes allows you to remove that subset of points. Plotting every possible pair of points for the first 10 principal components is displayed [here](pca_pairs.html). Colouring by the second level of the `path` column can be found [here](pca_of_rg.html).


<br>

```{r pca_12, echo=FALSE, warning=FALSE}

plot_MDS <- function(plot_results, PCx=1, PCy=2, phenotypes=plot_results$phenotypes, phenotypes_translation=plot_results$translation, colour=plot_results$level2cat)
{
	x <- list(title=paste("Principal component", PCx), zeroline = FALSE, showline = FALSE, showgrid = TRUE)
	y <- list(title=paste("Principal component", PCy), zeroline = FALSE, showline = FALSE, showgrid = TRUE)

	PCx <- as.numeric(plot_results[[paste0('evecs.', PCx)]] * sqrt(plot_results[['evals']][PCx]))
	PCy <- as.numeric(plot_results[[paste0('evecs.', PCy)]] * sqrt(plot_results[['evals']][PCy]))
	p <- plot_ly(x = PCx, y = PCy, type='scatter', mode='markers',
		hoverinfo='text', color = ~factor(colour),
		text = ~paste0(phenotypes, ' : ', phenotypes_translation), width=800, height=600) %>% layout(xaxis = x, yaxis = y)
	return(p)
}

load("../Rdata_outputs/pca.Rdata")

p <- div(plot_MDS(plot_results, 1, 2), colour=plot_results$finallevelcat, align='center')
p
```

<br>

```{r pca_34, echo=FALSE, warning=FALSE}
p <- div(plot_MDS(plot_results, 3, 4), colour=plot_results$finallevelcat, align='center')
p
```

<br>

```{r pca_56, echo=FALSE, warning=FALSE}
p <- div(plot_MDS(plot_results, 5, 6), colour=plot_results$finallevelcat, align='center')
p
```
</div>
