---
output: html_document
params:
  pheno: "50"
  dat: "../Rdata_outputs/geno_correlation_sig.Rdata"
  dat_male: "../Rdata_outputs/geno_correlation_male_sig.Rdata"
  dat_female: "../Rdata_outputs/geno_correlation_female_sig.Rdata"
  dat_across: "../Rdata_outputs/geno_correlation_across_sexes_sig.Rdata"
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(plotly)
require(crosstalk)
require(data.table)
require(dplyr)
require(DT)
require(kableExtra)
require(formattable)
require(htmltools)
# handle params
phen <- as.character(params$pheno)
print(phen)
load(params$dat)
dat_pheno <- geno_corr_df[.(params$pheno)]
load(params$dat_male)
dat_pheno_male <- geno_corr_df[.(params$pheno)]
load(params$dat_female)
dat_pheno_female <- geno_corr_df[.(params$pheno)]
load(params$dat_across)
dat_pheno_across <- geno_corr_df[.(params$pheno)]

ukcode <- strsplit(phen,"_")[[1]][1]
isICD <- is.na(as.numeric(ukcode))

both_sexes_defined <- TRUE
male_defined <- TRUE
female_defined <- TRUE

if(is.na(dat_pheno$description_p1[1])) {
	both_sexes_defined <- FALSE
} else {
	pheno_description <- dat_pheno_male$description_p1[1]
}

if(is.na(dat_pheno_male$description_p1[1])) {
	male_defined <- FALSE
} else {
	pheno_description <- dat_pheno_male$description_p1[1]
}

if(is.na(dat_pheno_female$description_p1[1])) {
	female_defined <- FALSE
} else {
	pheno_description <- dat_pheno_female$description_p1[1]
}


if (isICD) {
	ukb_url = "http://biobank.ctsu.ox.ac.uk/crystal/field.cgi?id=41202"
	ukcode = "41202"
} else {
	ukb_url = paste0("http://biobank.ctsu.ox.ac.uk/crystal/field.cgi?id=", ukcode)
}


create_barplot <- function(dat_pheno, params)
{
	div_colors <- c('blue','white','red')
	which <- order(dat_pheno$rg)[c(1:20, (nrow(dat_pheno)-80):nrow(dat_pheno))]
	dat_pheno <- dat_pheno[which,]
	dat_pheno$logp <- -log10(dat_pheno$p)
	dat_pheno$p2_tmp <- factor(paste0(dat_pheno$p2,':',dat_pheno$description_p2),
		levels = paste0(dat_pheno$p2,':',dat_pheno$description_p2)[order(dat_pheno$rg, decreasing = TRUE)])
	colfunc <- colorRampPalette(c("blue", "white", "red"))
	pal <- colfunc(1000)[round(ifelse(dat_pheno$rg< -1, 1, ifelse(dat_pheno$rg > 1, 1000, dat_pheno$rg*1000+1000)/2))]

	return(
		plot_ly(dat_pheno, height=400, width=800) %>%
				add_trace(
					x=~p2_tmp,
					y=~rg,
					marker = list(color =  pal),
					hoverinfo="text",
					text=~paste0(p1, " : ", p2, "\n",
						description_p1, " : ", description_p2, "\n",
						"Correlation : ", signif(rg, 3), "\n",
						"p-value: ", signif(p, 3)),
					type="bar"
		  ) %>% layout(
		  			 showlegend=FALSE,
		  			 xaxis = list(title="", tickangle=-90, automargin=TRUE, showticklabels=FALSE),
		  			 yaxis = list(title="$r_g$",side='left', range=c(-1,1))) %>% config(
		  			 mathjax = "cdn",
		  			 displaylogo = FALSE, collaborate = FALSE, showLink=FALSE, displayModeBar=FALSE, displaylogo=FALSE, sendData=FALSE)
	)
}

create_volcano_plot <- function(dat_pheno, params) 
{
	dat_pheno <- dat_pheno[.(params$pheno)]
	dat_pheno$logp <- -log10(dat_pheno$p)
	phenotypes_and_categories <- fread("../inputs/Fields_and_categories.tsv") %>% mutate(p2=as.character(FieldID))
	df_merge <- merge(dat_pheno, phenotypes_and_categories, by='p2', all.x=TRUE)
	
	where_ICD <- grep("main ICD10", df_merge$description_p2)
	df_merge$level2cat[where_ICD] <- "ICD10 code"
	df_merge$level2cat[where_ICD] <- "ICD10 code"
	
	where_finngen <- which(is.na(df_merge$level2cat))
	df_merge$level2cat[where_finngen] <- "FinnGen"
	df_merge$finallevelcat[where_finngen] <- "FinnGen"

	x <- list(title="Genotypic correlation ($r_g$)", zeroline = FALSE, 
		showline = FALSE, showgrid = TRUE, range=c(-1,1))
	y <- list(title="$-\\log_{10}(p)$", zeroline = FALSE, showline = FALSE, showgrid = TRUE)

	return(
		plot_ly(x = df_merge$rg, y = df_merge$logp, type='scatter', mode='markers',
			hoverinfo='text', color=df_merge$level2cat, height=400, width=800,
			text=~paste0(df_merge$p1, " : ", df_merge$p2, "\n",
				  	df_merge$description_p1, " : ", df_merge$description_p2, "\n",
				  	"Correlation : ", signif(df_merge$rg, 3), "\n",
				  	"p-value: ", signif(df_merge$p, 3))) %>% layout(xaxis = x, yaxis = y) %>% 
		config(mathjax = "cdn", displaylogo = FALSE, collaborate = FALSE, showLink=FALSE, displayModeBar=TRUE, displaylogo=FALSE, sendData=FALSE)
	)
}

create_table <- function(dat_pheno, params, phenotypic_corr=FALSE)
{
	dat_pheno <- dat_pheno[.(params$pheno)]
	ukcode <-  sapply(strsplit(dat_pheno$p2, split='_'),`[`, 1)
	isPHESANT <- grepl('^[0-9]', ukcode)
	uk_site <- ifelse(isPHESANT, paste0("http://biobank.ctsu.ox.ac.uk/crystal/field.cgi?id=", ukcode),
		"http://biobank.ctsu.ox.ac.uk/crystal/field.cgi?id=41202")
	n <- nrow(dat_pheno)
	n_tests <- n * (n-1) / 2
	bonf_thres <- 0.05 / n_tests
	nominal <- 0.05

	dat_pheno$p2_site <- ifelse(isPHESANT, paste0("<a href='", uk_site, "'>", dat_pheno$p2,"</a>"), dat_pheno$p2)
  	dat_pheno$description_p2 <- paste0("<a href='rg_summary_", dat_pheno$p2,".html'>", dat_pheno$description_p2,"</a>")
  	dat_pheno$description_p2 <- paste0("<a href='rg_summary_", dat_pheno$p2,".html'>", dat_pheno$description_p2,"</a>")
	if(phenotypic_corr) {
		dat_pheno <- dat_pheno %>% rename("ID" = p2_site, "Phenotype" = description_p2, "rp" = r2p) %>% select(c("ID", "Phenotype", "rg", "p", "rp"))
		return(
		dat_pheno %>% mutate(
			"rg" = ifelse(rg <= 0.0, color_tile("cornflowerblue", "transparent")(round(rg, 2)*c(rg<=0)),
								   color_tile("transparent", "indianred3")(round(rg,2)*c(rg>=0))),
			"rg p" = ifelse(p < bonf_thres, cell_spec(format(p, digits = 2), bold = TRUE),
	                   ifelse(p > nominal, cell_spec(format(p, digits = 2)),
	                   		  cell_spec(format(p, digits = 2), italic = TRUE))),
			"rp" = ifelse(rp <= 0.0, color_tile("cornflowerblue", "transparent")(round(rp, 2)*c(rp<=0)),
								   color_tile("transparent", "indianred3")(round(rp,2)*c(rp>=0)))) %>% select(c("ID", "Phenotype", "rg", "rg p", "rp")) %>% 
	    kable(escape=FALSE, align=c("l","l","c","c","c")) %>% kable_styling("hover", protect_latex=TRUE)
	)
	} else {
		dat_pheno <- dat_pheno %>% rename("ID" = p2_site, "Phenotype" = description_p2) %>% select(c("ID", "Phenotype", "rg", "p"))
		return(
		dat_pheno %>% mutate(
			"rg" = ifelse(rg <= 0.0, color_tile("cornflowerblue", "transparent")(round(rg, 2)*c(rg<=0)),
								   color_tile("transparent", "indianred3")(round(rg,2)*c(rg>=0))),
			"p" = ifelse(p < bonf_thres, cell_spec(format(p, digits = 2), bold = TRUE),
	                   ifelse(p > nominal, cell_spec(format(p, digits = 2)),
	                   		  cell_spec(format(p, digits = 2), italic = TRUE)))) %>% select(c("ID", "Phenotype", "rg", "p")) %>% 
	    kable(escape=FALSE, align=c("l","l","c","c")) %>% kable_styling("hover", protect_latex=TRUE)
	)
	}
}

```

<br>

## Genetic correlations with [`r pheno_description`](`r ukb_url`) {.tabset .tabset-fade}

Genetic correlation is estimated using [LD-score regression](https://github.com/bulik/ldsc). Full details of the correlation estimator can be found [here](https://www.ncbi.nlm.nih.gov/pubmed/26414676). In the tables, $r_g$ is the genetic correlation, and \(r_p\) is the phenotypic correlation.

### All {.tabset}

[//]: # <div id="all_bar" class="section level4">
[//]: # #### Bar plot
[//]: # 
[//]: # ```{r make_bar_plot_all, echo=FALSE}
[//]: # 
[//]: # div(create_barplot(dat_pheno, params), align='center')
[//]: # 
[//]: # ```
[//]: # 
[//]: # </div>

<div id="all_volcano" class="section level4">
#### Volcano plot

```{r make_volcano_plot_all, echo=FALSE, warning=FALSE}
if(both_sexes_defined)
	div(create_volcano_plot(dat_pheno, params), align='center')
```

</div>


<div class="well">

```{r make_all_table, echo=FALSE}
if (both_sexes_defined)
	create_table(dat_pheno, params, phenotypic_corr=TRUE)
```

`r ifelse(both_sexes_defined,'','This phenotype is not significant or does not make sense for both sexes.')`

</div>

### Males {.tabset}

[//]: # <div id="male_bar" class="section level4">
[//]: # #### Bar plot
[//]: # 
[//]: # ```{r make_bar_plot_male, echo=FALSE}
[//]: # 
[//]: # div(create_barplot(dat_pheno_male, params), align='center')
[//]: # 
[//]: # ```
[//]: # 
[//]: # </div>

<div id="male_volcano" class="section level4">
#### Volcano plot

```{r make_volcano_plot_male, echo=FALSE, warning=FALSE}
if(male_defined)
	div(create_volcano_plot(dat_pheno_male, params), align='center')
```

</div>


<div class="well">

```{r make_male_table, echo=FALSE}
if(male_defined)
	create_table(dat_pheno_male, params)
```

`r ifelse(male_defined,'','This phenotype is not significant or does not make sense for males.')`

</div>

### Females {.tabset}

[//]: # <div id="female_bar" class="section level4">
[//]: # #### Bar plot
[//]: # 
[//]: # ```{r make_bar_plot_female, echo=FALSE}
[//]: # 
[//]: # div(create_barplot(dat_pheno_female, params), align='center')
[//]: # 
[//]: # ```
[//]: # 
[//]: # </div>

<div id="female_volcano" class="section level4">
#### Volcano plot

```{r make_volcano_plot_female, echo=FALSE, warning=FALSE}
if(female_defined)
	div(create_volcano_plot(dat_pheno_female, params), align='center')
```

</div>

<div class="well">

```{r make_female_table, echo=FALSE}
if(female_defined)
	create_table(dat_pheno_female, params)
```

`r ifelse(female_defined,'','This phenotype is not significant or does not make sense for females.')`

</div>

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
    $(document).ready(function() {
        $("table").DataTable();
    } );
</script>
